method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update method.Rmd

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
<!--JZ: Hast du ED schon als Abkürzung eingeführt?--> The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

>>>>

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).<!-- This results in two digit numbers, with the last digit being zero. Perhaps use papaja::printnun(x, diguts = 1, gt1 = T) instead, this rounds up to 1 digit, but also only displays one digit (at least I hope so) -->
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
<!--JZ: Hast du ED schon als Abkürzung eingeführt?--> The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
